### 2020-07-19 Manuscript.Rmd
added pdf

Next, we were interested in branch level patterns of expression, focusing on whether change in expression across the same branch in a gene tree is correlated between different zooids. We investigated the co-variance structure of changes across particular branches (that correspond to species tree branches) within gene trees among different zooids/the pneumatophore (Figs. \@ref(fig:covariances)). For change across the same branch within a gene tree that corresponds to a particular branch in the species tree, there is a positive correlation between pairwise comparisons of zooids/the pneumatophore. In particular, changes across all branches are highly correlated between developing and mature gastrozooids. Changes in expression across the same branch were also highly correlated between gastrozooids and palpons, especially so across branches corresponding to branch K (\@ref(fig:changes), top panel) in the species tree (branch leading to *Agalma elegans*).  Meanwhile, changes across all branches are much less correlated between any zooid/the pneumatophore and both the male or female gonodendra. These results suggest that changes in expression across gene tree branches are highly correlated among zooids - a large positive change in expression in one zooid across a gene tree branch that corresponds to branch L,  for example, will also typically see a large positive change in expression in another zooid across the same branch.

@@

We were then able to identify instances of branches in gene trees where change in expression across the branch is negatively or positively correlated among different gene trees. One such example of lineage and zooid specific changes in expression is in a putative hydrozoan specific actinoporin-like gene family, with closest blast similarity to Auger and Cone snail tereporin/coroporin toxins. In this toxin-like family, we were able to identify one clade (clade Y, Fig. \@ref(fig:venom-plot)) with three branches corresponding to branches K, L and I in the species tree. The branches that correspond to I and K, leading to a *Diphyes dispar* and *Agalma elegans* gene respectively, both have large increases in mature gastrozooid expression across the branch, while the branch that corresponds to branch L (leading to *Nanomia bijuga*) has a large decrease in expression across the branch in mature gastrozooids and an independent large increase in expression for the same branch in mature palpons. For all other zooids/tissues the expression at the tips is close to 0, with only small changes in expression across the branch. In *Nanomia bijuga* the gene 976500 in Clade Y is significantly differentially expressed in mature palpons as compared to mature gastrozooids (log2 Fold Change 6.83224, Bonferroni adjusted p-value 0.000567528). These results point towards a lineage and zooid specific change in expression.

@@

(ref:venom-plot) Pruned maximum likelihood gene tree of a venom gene family found in siphonophore species with expression values (TPM10K) at the tips and nodes. Mature gastrozooid expression in orange (above node), palpon expression in yellow (below node). Changes in expression across the branch are found in black boxes along the branch, orange = mature gastrozooid, yellow = mature  palpon. Red circles are duplication nodes and blue circles are speciation nodes.

@@

```{r fullvenom-plot, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.height=15, fig.width=15, fig.cap='(ref:wnt-fullvenom)', fig.align = 'center'}

>>>>

Next, we were interested in branch level patterns of expression, focusing on whether change in expression across the same branch in a gene tree is correlated between different zooids. We investigated the co-variance structure of changes across particular branches (that correspond to species tree branches) within gene trees among different zooids/the pneumatophore (Figs. \@ref(fig:covariances)). For change across the same branch within a gene tree that corresponds to a particular branch in the species tree, there is a positive correlation between pairwise comparisons of zooids/the pneumatophore. In particular, changes across all branches are highly correlated between developing and mature gastrozooids. Changes in expression across the same branch were also highly correlated between gastrozooids and palpons, especially so across branches corresponding to branch K (\@ref(fig:changes), top panel) in the species tree (branch leading to *Agalma elegans*).  Meanwhile, changes across all branches are much less correlated between any zooid/the pneumatophore and both the male or female gonodendra. These results suggest that with the exception of male and female gonodendra, in general changes in expression across gene tree branches are highly correlated among zooids - a large positive change in expression in one zooid across a gene tree branch will also typically see a large positive change in expression in another zooid across the same branch.

@@

We were then able to identify instances of branches in gene trees where change in expression across the branch is negatively or positively correlated among different zooids. One example of possible lineage and zooid specific changes in expression across a branch is found in a putative hydrozoan specific actinoporin-like gene family, with closest blast similarity to Auger and Cone snail tereporin/coroporin toxins. In this toxin-like family, we were able to identify one clade (clade Y, Fig. \@ref(fig:venom-plot), Fig. \@ref(fig:fullvenom-plot)) with three branches corresponding to branches K, L and I in the species tree. The branches that correspond to I and K, leading to a *Diphyes dispar* and *Agalma elegans* gene respectively, both have large increases in mature gastrozooid expression across the branch, while the branch that corresponds to branch L (leading to *Nanomia bijuga*) has a large decrease in expression across the branch in mature gastrozooids and an independent large increase in expression for the same branch in mature palpons. For all other zooids/tissues the expression at the tips is close to 0, with only small changes in expression across the branch. In *Nanomia bijuga* the gene 976500 in Clade Y is significantly differentially expressed in mature palpons as compared to mature gastrozooids (log2 Fold Change 6.83224, Bonferroni adjusted p-value 0.000567528). These results point towards a lineage and zooid specific change in expression across branch L leading to an actinoporin-like gene homolog in *Nanomia bijuga*.

@@

(ref:venom-plot) Pruned maximum likelihood gene tree of a putative actinoporin-like gene family found in siphonophore species with expression values (TPM10K) at the tips and nodes. Mature gastrozooid expression in orange (above node), palpon expression in yellow (below node). Changes in expression across the branch are found in black boxes along the branch, orange = mature gastrozooid, yellow = mature  palpon. Red circles are duplication nodes and blue circles are speciation nodes.

@@

```{r fullvenom-plot, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.height=15, fig.width=15, fig.cap='(ref:fullvenom-plot)', fig.align = 'center'}
